\chapter{Conclusion and Future work}\label{cap:conclusion}

\section{Conclusion}
To sum up the results of the thesis, the Android application RealityEnhance meets the goals that were set at the beginning of the project. The application gives the user the power of an enhance perception of their surroundings by placing \ac{3D} models in the real world. The application has a simple and intuitive user interface that allows it to have many application in a wide range of domains. It also shows the potential of \ac{AR} in the field of education. RealityEnhance can be used as a didactic tool for the teachers, by giving students the possibility to interact with the models in the \ac{AR} mode.

The application will be available for Android devices and it is free to download from the Google Play Store. The application will also be available for IOS devices in the future. All the code of the application is available on GitHub\cite{RealityEnhance} and it is open source.



\section{Future work}
In this section we will present the future work that will be done to improve the application.
A list of future improvements and features that will be added to the application:
\begin{enumerate}
    \item{Provide more models in the library}
    \item{Store all the information about a model in a QR code}
    \item{Make the application available for IOS}
    \item{Develope a platform that allows users to upload their own models}
    \item{Add a feature that allows user to save a scene with the placed models}
\end{enumerate}
