\chapter{Related Work }\label{cap:relatedwork}
\section{Related writings}
Deeper Learning With QR Codes and Augmented Reality: A Scannable Solution for Your Classroom
\section{Related apps}

\subsection{Snapchat AR}
Snap AR enables creators around the world to revolutionize the way we create, explore, and play. The AR Bar has special Lenses and helps you scan the world for useful info! Tap the Camera screen to open the AR Bar. The AR Bar has the following options: Create: Choose from a selection of special Lenses you can edit and change!

Snapchat has continued to democratize the process of creating AR Lenses with their Web Lens Builder and Lens Studio tools. With the addition of real-world physics and real-time data integrations, they've improved the realism of their AR to offer a more immersive experience.

Pros:

Wide range of special Lenses to choose from
Real-world physics and real-time data integrations improve the realism of AR
Web Lens Builder and Lens Studio tools make it easy for creators to make their own Lenses
Cons:

May require a permanent internet connection
Limited functionality compared to other AR apps
\subsection{Pokemon Go}
LINK: \href{https://niantic.helpshift.com/hc/en/6-pokemon-go/faq/28-catching-pokemon-in-ar-mode/}{Pokemon Go AR mode}
AR+ mode is an enhanced version of Pokémon GO’s augmented reality feature in which Pokémon appear anchored to your real-world environment right in front of you. You can walk right up to a Pokémon for a chance at an Excellent Throw bonus or the perfect photo opportunity. Pokémon are aware of your movement, so proceed with caution. Move toward a Pokémon too fast and you’ll scare it away...but approach slowly, and you’ll have a better chance at catching it.

AR+ mode displays Pokémon fixed to a point in your real-world environment. Pokémon appear on the ground in front of you. You can walk toward or around the Pokémon. Pokémon have awareness of how close you are and how fast you are moving toward them.

AR MODE:
Pokémon are not fixed to your real-world environment in AR mode. Pokémon do not have awareness of the Trainer’s location or movement.

Pros:

Enhanced AR feature with fixed point of Pokémon in real-world
Pokémon have awareness of player's location and movement
Excellent Throw bonus and photo opportunity for players
Cons:

May require a permanent internet connection
Limited functionality compared to other AR apps
\subsection{ARFICIO}
This app is similar with what I'm trying to do but is partially free and doesn't have the same features as I want to have. I believe that you need to have a permanent connection to the internet.

Pros:

Partially free
Cons:

Limited features compared to what I am trying to do
Permanent internet connection may be required
LINK: \href{https://arficio.com/pricing/}{ARFICIO pricing}

Note: To find more documentation on ARFICIO and other AR apps, you may want to search for articles and reviews online or visit the official website of the app.